---
title: "ILoReg S4 package example"
output: html_notebook
---



```{r}
data <- Seurat::LogNormalize(Seurat::Read10X("~/../Downloads/10x_data/pbmc3k/filtered_gene_bc_matrices_GRCh37.p13/hg19/"))
```


```{r}
library(ILoReg)
iloreg_object <- CreateILoRegObject(normalized.data = data)
```


```{r}
iloreg_object <- RunILoRegConsensus(iloreg_object,threads = 3,L = 50)
```


```{r}
VisualizeConsensusInformation(iloreg_object)
```

Run PCA and tSNE or UMAP
```{r}
iloreg_object <- ILoReg::RunPCA(iloreg_object,number.of.pcs = 50,scale = FALSE)
iloreg_object <- ILoReg::RunUMAP(iloreg_object)
iloreg_object <- ILoReg::RunTSNE(iloreg_object,perplexity=30)
```


Hierarchical clustering
```{r}
iloreg_object <- HierarchicalClustering(iloreg_object)
```


Calculate silhouette information for K in 2:50
```{r}
iloreg_object <- CalculateSilhouetteInformation(iloreg_object,k.range = 2:50)
SilhouetteCurve(iloreg_object)
```

Select K=20 clusters from the dendrogram
```{r}
iloreg_object <- ManualClustering(iloreg_object,K=20)
```




```{r}
GeneScatterPlot(iloreg_object,"CD8B",dim.reduction.type = "umap")
GeneScatterPlot(iloreg_object,"CD8B",dim.reduction.type = "tsne")
```

Visualize tSNE and UMAP transformations with the two clusterings
```{r}
ClusterScatterPlot(iloreg_object,"optimal",dim.reduction.type = "umap")
ClusterScatterPlot(iloreg_object,"manual",dim.reduction.type = "umap")
ClusterScatterPlot(iloreg_object,"optimal",dim.reduction.type = "tsne")
ClusterScatterPlot(iloreg_object,"manual",dim.reduction.type = "tsne")
```

Merge two clusters
```{r Fig4, echo=TRUE, fig.height=7, fig.width=14}
p1 <- ClusterScatterPlot(iloreg_object,"manual",dim.reduction.type = "umap",return.plot = T)+ggplot2::ggtitle("Before merging 10 and 9")
iloreg_object <- MergeClusters(iloreg_object,clusters.to.merge = c(10,9))
p2 <- ClusterScatterPlot(iloreg_object,"manual",dim.reduction.type = "umap",return.plot = T)+ggplot2::ggtitle("After merging 10 and 9")
cowplot::plot_grid(p1,p2)
```


```{r}
ClusterScatterPlot(iloreg_object,"manual",dim.reduction.type = "umap")
iloreg_object <- RenameClusters(iloreg_object,new.cluster.names = LETTERS[1:iloreg_object@K.manual])
ClusterScatterPlot(iloreg_object,"manual",dim.reduction.type = "umap")
```

Find gene markers for the automatic clustering
```{r}

gene_markers <- FindAllGeneMarkers(iloreg_object,
                                   clustering.type = "manual",
                                   test = "wilcox",
                                   logfc.threshold = 0.25,
                                   min.pct = 0.25,
                                   min.diff.pct = 0.25,
                                   pseudocount.use = 1,
                                   min.cells.cluster = 3,
                                   return.thresh = 0.01,
                                   only.pos = FALSE)

```

Find gene markers for clusters C and R from the manual clustering
```{r}

gene_markers_C_R <- FindGeneMarkers(iloreg_object,clusters.1 = "C",clusters.2 = "R",
                                   clustering.type = "manual",
                                   test = "wilcox",
                                   logfc.threshold = 0.25,
                                   min.pct = 0.25,
                                   min.diff.pct = 0.25,
                                   pseudocount.use = 1,
                                   min.cells.cluster = 3,
                                   return.thresh = 0.01,
                                   only.pos = FALSE)

```


Select top 10 and top 3 genes based on log2 fold-change
```{r}
library(dplyr)

gene_markers %>% group_by(cluster) %>% top_n(10, log2FC) -> top10
gene_markers %>% group_by(cluster) %>% top_n(3, log2FC) -> top3
```


Make gene scatter plots
```{r Fig1, echo=TRUE, fig.height=20, fig.width=20}
cowplot::plot_grid(plotlist = lapply(unique(top3$gene),function(x) GeneScatterPlot(iloreg_object,x,dim.reduction.type = "umap",return.plot = T)))
```


```{r Fig2, echo=TRUE, fig.height=20, fig.width=40}
VlnPlot(iloreg_object,clustering.type = "manual",genes = unique(top3$gene))
```

Make gene heatmap
```{r Fig5, echo=TRUE, fig.height=15, fig.width=15}
GeneHeatmap(iloreg_object,clustering.type = "manual",gene.markers = top10)

```

